Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-08 wsdm-2017/source/paper.tex
Revise partial trust figure. Use theorem/proof format.

\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

@@

\begin{figure}
\centerline{\includegraphics[width=2.12in,height=1.46in]{fig-alice_trusted_neigh2}}
\caption{
Illustration of the {\em partial trust} model.
Edges represent direct, mutual trust relationships.
Alice ($v$) trusts all nodes less than
$h$ hops away---her {\em trusted neighborhood} $T_h(v)$.
Beyond that, the nodes at distance $h$ form her {\em trust boundary} $B_h(v)$.
We assume adversaries are unable to compromise nodes in the trusted neighborhood.
By compromising all nodes in the trust boundary, an adversary can ensure that
all communications leaving Alice's trusted neighborhood are compromised.
}
\label{fig:trust-source}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=3.33in,height=1.46in]{fig-bob_Alice_trusted_neigh2}}
\caption{
Partial trust model with sender (Alice) and receiver (Bob).
If disjoint paths exist connecting each node in Alice's trust boundary to
a node in Bob's,
than an adversary needs to compromise at least $|T_h(v)|$ nodes to
compromise all possible paths between Alice and Bob.
}
\label{fig:trust-source-destionation}
\end{figure}

@@

The wrap-around butterfly network has a number of properties desirable for
a scalable, decentralized communication network:
\begin{description}
\item[Vertex-transitivity:]
Because the wraparound butterfly is vertex transitive,
it is maximally decentralized;
\item[Small-diameter:]
For any two nodes, the length of the shortest path between them is
$O(\log N)$, where N is the number of nodes in the network;
\item[Sparsity:]
With a constant degree of 4, the wraparound butterfly is extremely sparse,
and can scale indefnitely without node degree becoming a limitation;
\item [Redundancy:]
The number of independent paths between two
nodes in the wraparound butterfly increases exponentially in the trust
radius $h$ (the routing algorithm below constructs thes explicitly).
\end{description}

@@

We now formally specify the multipath routing scheme and prove
that provides $2^h$ disjoint paths between
the $h$-hop trusted neighborhoods of any two nodes in an $m$-bit
wrap-around butterfly network.
Utilizing vertex transitivity, we label the source node as
$(l^{(0)}, z^{(0)}) = (0, 0)$ and denote the destination node as $w = (l_w, z_w)$,
without loss of generality.

@@

For all $2^h$ of these paths, the components excluding nodes within $h$ hops
of $v$ or $w$ (in their trusted neighborhoods) are pairwise disjoint,
which we now prove.
Nodes from two paths can only coincide if their levels are the same.
Nodes which share a level must either be in the same stage, or 4 stages
apart.
Let ($a$,$a^\prime$) denote a pair of sub-paths corresponding to stage $a$ of
one path and stage $a^\prime$ of another.
Excluding paths that intersect in their trusted neighborhoods, (1,1) and (7,7),
we have reduced the list of possible intersections to the following cases:
(2,2), (3,3), (4,4), (5,5), (6,6), (1,5), (2,6), and (3,7).
Nodes in stages 2--4 belong to $R_s$ so cannot overlap with any stage 2--4
nodes from another path, eliminating (2,2), (3,3), and (4,4).
Similarly, nodes in stages 4--6 belong to a unique $S_s$,
eliminating (5,5) and (6,6).
Nodes in stage 1 belong to $Q_{v^{(0)}}$ while those in stage 5 belong in
its complement, eliminating (1,5).
Similarly, for all $l$ in stage 2, $z^{(l)}$ is equal to $z^{(0)}$,
while in stage 6, $z^{(l)}$ is the inverse, eliminating (2,6)
This leaves only (3,7), a collision which can occur only for only one path
(with $s$ matching the first $h$ bits of $z_w$), and which enters the trusted
neighborhood in stage 3.
For this single path, we can proceed directly from stage 2 to stage 7,
eliminating the last possible collision.

Thus, we have shown that assuming the partial trust model, with trust transitive
for $h$ hops, we can construct $2^h$ paths on a wraparound butterfly topology
which do not intersect outside the trusted neighborhoods of the source and
destination.
This is a lower bound on the value $B$ in Equation (\ref{eq:pf}),
showing that the decentralized, redundant, structured networks such as the
butterfly can have a very low probability of failure when faced with
adverarial faults, even from a very powerful attacker.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}
\newtheorem{theorem}{Theorem}

@@

\begin{figure}
\centerline{\includegraphics[width=3in,height=2.08in]{fig-partial-trust}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em partial trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $v$) and receiver (Bob, $w$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can be modelled as connected by a direct link with
at least $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

The wrap-around butterfly network is known to have several of the properties
we desire for scalable, decentralized communication networks:
\begin{description}
\item[Vertex-transitivity:]
Because the wraparound butterfly is vertex transitive,
it is maximally decentralized;
\item[Small-diameter:]
For any two nodes, the length of the shortest path between them is
$O(\log N)$, where N is the number of nodes in the network;
\item[Sparsity:]
With a constant degree of 4, the wraparound butterfly is extremely sparse,
and can scale indefnitely without node degree becoming a limitation;
\item [Redundancy:]
Multiple paths exist between any two nodes.
Specifically, we will prove below that the number of independent paths between two
nodes increases exponentially with the trust
radius $h$.
\end{description}

@@

We now begin the formal specification of our multipath routing scheme for the
wraparound butterfly network.
Utilizing vertex transitivity, we label the source node as
$(l^{(0)}, z^{(0)}) = (0, 0)$ and denote the destination node as $w = (l_w, z_w)$,
without loss of generality.

@@

\begin{theorem}
Given an $m$-bit wraparound ($m \geq 0$) butterfly network,
and a trust radius $h \geq 1$,
for all node pairs $(v, w)$,
if there exists a node $u$ that belongs to
two distinct routes $v^{(\cdot)}_s$ and $v^{(\cdot)}_{s^\prime}$
($s \neq s^\prime$),
it implies that $u \in T_h(v) \cup T_h(w)$.
\end{theorem}
\begin{proof}
Nodes from two paths can only coincide if their levels are the same.
Nodes which share a level must either be in the same stage, or 4 stages
apart.
Let ($a$,$a^\prime$) denote a pair of sub-paths corresponding to stage $a$ of
one path and stage $a^\prime$ of another.
Excluding paths that intersect in their trusted neighborhoods, (1,1) and (7,7),
we have reduced the list of possible intersections to the following cases:
(2,2), (3,3), (4,4), (5,5), (6,6), (1,5), (2,6), and (3,7).
Nodes in stages 2--4 belong to $R_s$ so cannot overlap with any stage 2--4
nodes from another path, eliminating (2,2), (3,3), and (4,4).
Similarly, nodes in stages 4--6 belong to a unique $S_s$,
eliminating (5,5) and (6,6).
Nodes in stage 1 belong to $Q_{v^{(0)}}$ while those in stage 5 belong in
its complement, eliminating (1,5).
Similarly, for all $l$ in stage 2, $z^{(l)}$ is equal to $z^{(0)}$,
while in stage 6, $z^{(l)}$ is the inverse, eliminating (2,6)
This leaves only (3,7), a collision which can occur only for only one path
(with $s$ matching the first $h$ bits of $z_w$), and which enters the trusted
neighborhood in stage 3.
For this single path, we can proceed directly from stage 2 to stage 7,
eliminating the last possible collision.
\end{proof}

Thus, assuming the partial trust model with trust transitive
for $h$ hops, we can construct $2^h$ paths on a wraparound butterfly topology
which do not intersect outside the trusted neighborhoods of the source and
destination.
Note that the node sequence $v_s^{(t)}$ can be calculated entirely
from the source $v$, destination $w$, and path parameter $s$,
meaning that with this informaiton nodes are able to determine which neighbor
to route a given message copy to.
Furthermore, the existence of $2^h$ paths places a lower bound on the
effective redundancy $\delta_h$,
showing that the decentralized, redundant, structured networks such as the
butterfly can have a very low probability of failure when faced with
adverarial faults, even from a very powerful attacker.
